Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
updating the formalization

\tias{Use generic constraint}
A \textit{Spreadsheet constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}. Let us elaborate on each of them. \textit{\CName} is the textual name of the constraint together with its variable names. \textit{\CSignature} is a set of constraints specifying the properties of the group assignments, corresponding to the variables in \CName, such as their types, e.g., requiring them to be integers or constraining the sizes, e.g. the length of vectors in the arguments must be equal. These are constraints on the group meta-information not on the actual group content. \textit{\CFunction} is a set of constraints specifying that the data in the subgroups satisfies the function. For example, a spreadsheet constraint \textit{rank} has \CName \textit{Y = RANK(X)}, where $X$ and $Y$ are the variables; its \CSignature is: the group $G_X$ (associated with X) is numeric, $G_Y$ is integer and the length of vectors in $G_X$ is the same as in $G_Y$; its \CFunction is the following constraint: a pair of vectors $X,Y$ is a solution iff $X \in G_X, Y \in G_Y$ and each value in $X$ has the rank (possibly with ties) specified in $Y$.

@@

A \textit{tabular solution} $S$ to a spreadsheet constraint $C$ is a tuple $(X_1, \dots, X_n)$ where $n$ is the number of variables in $C$ and each $X_i$ is a subgroup in \groups, such that $(X_1,\dots,X_n)$ satisfies both the \CSignature and \CFunction of the constraint $C$.

>>>>

\tias{Use generic constraint}
A \textit{Spreadsheet constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}. Let us elaborate on each of them. \textit{\CName} is the textual name of the constraint together with its variable names. \textit{\CSignature} is a set of constraints specifying the properties of the group assignments, corresponding to the variables in \CName, such as their types, e.g., requiring them to be integers or constraining the sizes, e.g. the length of vectors in the arguments must be equal. These are constraints on the group meta-information not on the actual group content. \textit{\CFunction} is a set of constraints specifying that the data in the subgroups satisfies the function. For example, a spreadsheet constraint \textit{rank} has \CName \textit{$g_Y$ = RANK($g_X$)}, where $g_X$ and $g_Y$ are the variables; its \CSignature is: the subgroup $g_X$ (associated with X) is numeric, $g_Y$ is integer and the length of vectors in $g_X$ is the same as in $g_Y$; its \CFunction is the following constraint: a pair of vectors $g_X,g_Y$ is a solution iff $g_X \in G_X, g_Y \in G_Y$ and each value in $g_X$ has the rank (possibly with ties) specified in $g_Y$.

@@

A \textit{tabular solution} $S$ to a spreadsheet constraint $C$ (with $n$ variables) is a subgroup assignment $(g_1, \dots, g_n)$ where $g_i$, such that $(g_1,\dots,g_n)$ satisfies both the \CSignature and \CFunction of the constraint $C$. \sergey{to finish this definition later, need to say that $g_i$ is the subgroup assigned to the $i$-th variable in $C$}
